\documentclass{article}
\usepackage{graphicx}
\usepackage{amsfonts}

\begin{document}

\title{Homework 14}
\author{Josh Cai}

\maketitle
\begin{enumerate}
\item
Let $\{x\} \subset X$ and $\{y\} \subset Y$ be arbitrary. Then $X-\{x\}$ is open and $Y-\{y\}$ is open, because $\{x\}, \{y\}$ are closed since $X, Y$ are $T_1$ spaces. Thus, $X-\{x\} \times Y-\{y\}$ is open in $X \times Y$. Thus $X \times Y - (X-\{x\} \times Y-\{y\}) = \{x\} \times \{y\}$ is closed. Since $x, y$ arbitrary, one point sets are closed in $X \times Y$ and $X\times Y$ is a $T_1$ space.

\item 
Let $x\in S$. Then $S - \{x\}$ is closed because closedness is preserved under finite union ($S - \{x\}$ is a finite subset since $S$ is a finite subset). Thus, $X - (S - \{x\}) = (X-S) \cup \{x\}$ is open, which is a neighborhood of $x$ that does not intersect $S$ at any point other than $x$ itself. Thus, $x$ is not a limit point. Since $x$ is arbitrary, there cannot be any limit points in $S$.

\item
($\Rightarrow$) $X-\{x\}$ is an open set, since $\{x\}$ is closed. Thus, $X-\{x\}$ is an open neighborhood of $y$ that does not contain $x$. $x-\{y\}$ is an open set, since $\{y\}$ is closed. Thus, $X-\{y\}$ is an open neighborhood of $x$ that does not contain $y$.
\\\\($\Leftarrow$) Let $x \in X$ be arbitrary. Then for every point in $X-\{x\}$ there is a neighborhood not containing $x$ by supposition. The union of these neighborhoods is clearly contained in $X-\{x\}$ since each neighborhood is a subset of $X-\{x\}$. $X-\{x\}$ is contained within the union of these neighborhoods because every $y \in X-\{x\}$ is in the neighborhood of $y$. Thus, $X-\{x\}$ is a union of open sets, so $X-\{x\}$ is open. Then $X - (X-\{x\}) = \{x\}$ is closed. Since $x$ is arbitrary, one point sets are closed in $X$, and $X$ is a $T_1$ space.


\end{enumerate}
\end{document}